### 2017-09-29 TF-vldb2018/sec-tsimAlg.tex

\stitle{Pattern satisfiability}.
Different from graph simulation \cite{infsimu95} and its extensions \cite{FanLMTWW10,MaCFHW14},
there exist pattern graphs that do not match any data graph via team simulation, due to the presence of capacity constraints enforced on patterns. We illustrate this with an example below.
%\looseness=-1

@@

By treating $P$ as both data and pattern graphs, compute the maximum match relation $M$ in $P$ for $P$, via graph simulation.
Then pattern $P$ is satisfiable iff for each $(u, v)\in M$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, $x_v \leq y_u$ holds. Observe that the size of $M$ is bounded by $|P|^2$, and pattern graphs are also small.

@@

\revise{
\stitle{Incremental computing for radius varied balls}. Recall that given $G$, $P$, $k$ and $r$, \teamF\,is to find top-$k$ teams within balls $\ball{[v, t]}$, where $v \in V$ and $t \in [1,r]$.
%centered at each node in $G$ with radius $t$ varying from 1 to $r$.
However, it is extremely costly to construct all such balls, \ie $r\cdot|V|$ balls, to compute perfect subgraphs residing in them.
Instead, \grouprec only constructs and computes the matches for a number of $|V|$ balls, \ie the set of balls $\ball{[v, r]}$
where $v \in V$ and radius is $r$ ,
and then incrementally computes the perfect subgraphs for balls $\ball{[v, t]}$ ($t \in [1,r-1]$) from the match graphs for ball $\ball{[v, r]}$ who shares the same center node. The correctness of \grouprec is assured by the theorem below.

@@

When we get the match graph $G_s$ in $\ball{[v, r]}$ for $P$ via graph simulation, to compute the perfect subgraph in $\ball{[v, t]}$ ($t \in [1,r-1]$) for $P$ via team simulation, we need to
(1) first identify the subgraph $G_s^{t}$ in $G_s$ belonging to $\ball{[v, t]}$, which can be easily identified in the process for constructing $\ball{[v, r]}$ without extra computation;
(2) check whether $G_s^{t}$ is already a match graph for $P$ in $\ball{[v, t]}$ via graph simulation; if not, remove the unmatched nodes and edges from $G_s^{t}$ until find the match graph $G'_s$ for $P$ in $\ball{[v, t]}$. This can be achieved by executing an efficient incremental process in~\cite{FanWW13-tods}; and
(3) finally check whether capacity bounds are satisfied. If so, $G'_s$ is the perfect subgraph in $\ball{[v, r]}$ for $P$ via team simulation.}

\stitle{Density based filtering}. Although we have reduced a significant amount of computation by only computing team simulation for a number of $|V|$ balls by the incremental optimization above, we can further optimize the process by adopting the density based filtering technique.
%A typical idea to devise algorithms for \teamF\, is to compute the perfect subgraph within each ball and maintains the top-$k$ non-repeated perfect subgraphs with current top-$k$ largest density, and returns them when all balls are processed.
%This technique allows algorithm \grouprec to compute the top-$k$ perfect subgraphs \wrt $P$ without necessarily computing team simulation for all balls in $G$.
It allows \grouprec to compute team simulation for much less than $|V|$ balls.
The crucial issue is how can tell whether a ball has the possibility to have one of the final top-$k$ results in itself or in its inner balls with the same center node.
%If the answer is yes, we should check team simulation for that ball; Otherwise, we just skip the ball to the remaining balls.
The idea is, given a ball $\ball{[v,r]}$, we calculate the upper bound of $\density{\hat{G}_s}$,
where $\hat{G}_s$ is a subgraph of $\ball{[v,r]}$.
If the bound is larger than the current $k$-th result, \ie there is possibility the final answer resides in the ball or the inner balls, compute team simulation for it;
Otherwise, skip the ball to the remaining balls to avoid redundant team simulation computing.

The problem here is how to efficiently compute the upper bound of $\density{\hat{G}_s}$ for each ball in $G$.
As the best densest subgraph algorithms are in $O(|\ball{[v,r]}|^3)$ time \cite{maximumDenseSubgraph}, which is costly,
we utilize an important result in~\cite{EVMK12}, shown below.

@@

We are now ready to present algorithm \grouprec for \teamF{}.

\revise{
\stitle{Algorithm \grouprec.} As shown in Fig.~\ref{alg-grouprec}, it takes input as $P$, $G$, and two integers $r$ and $k$, and outputs the top-$k$ densest perfect subgraphs in $G$ for $P$.
It firstly checks whether $P$ is satisfiable (line 1).
If so, for each ball $\ball{[v,r]}$ in $G$, it computes the maximum core $\ball{}_{C}$ of $\ball{[v,r]}$, and checks whether the early termination condition holds (lines 3-6).
If so, it returns the current top-$k$ densest perfect subgraphs as top-$k$ teams;
otherwise, it computes the perfect subgraph $G_{s}$ of $P$ in $\ball{[v,r]}$ via team simulation by invoking \rgraphsim (line 7, see full version~\cite{fullvldb18}),
an adaption from graph simulation~\cite{infsimu95,FanLMTWW10} and checking capacity bounds (line 8).
It then computes perfect subgraphs $G'_{s}$ of $P$ in inner balls $\ball{[v,t]}$ by invoking \incsim, an extension of the data incremental algorithms in \cite{FanWW13-tods} and checking capacity bounds (lines 9-11).}
%Procedure \rgraphsim is deferred to the appendix, which is an adaption from graph simulation~\cite{infsimu95,FanLMTWW10}.}
%by extending from directed to undirected graphs,  incorporating the capacity constraint check, and only maintaining the capacity bounds satisfied perfect subgraphs.

\stitle{Correctness \& complexity analyses}. The correctness of \grouprec is assured by the following.
%(1) There is a unique perfect subgraph in each ball of $G$.
(1) The correctness of \rgraphsim (resp. \incsim) can be verified along the same lines as for simulation~\cite{infsimu95} (resp. incremental simulation \cite{FanWW13-tods}).
(2) Theorem~\ref{thm-tsim-radius} and Lemma~\ref{lemma-approximation-bound}.
\warn{
It takes $O(|P|^2)$ to check pattern satisfiability, $O(|V||P||G|)$ to compute team simulation, $O(r|V||V_{P}||E|)$ to incrementally compute matches in inner balls, and $O(|V||E|)$  to compute the density of the maximum core for $|V|$ balls.
Thus \grouprec is in $O(|P|^2+|V||P||G|+r|V||V_{P}||E|)$. However, actual time is much less due to early termination and that  $O(r|V||V_{P}||E|)$ is the worst case complexity for incremental process, while $r$ is small, \ie 2 or 3.}
\looseness=-1

>>>>

\subsection{Pattern Satisfiability}
Different from graph simulation \cite{infsimu95} and its extensions \cite{FanLMTWW10,MaCFHW14},
there exist pattern graphs match no data graphs via team simulation, due to the presence of capacity constraints on patterns. We illustrate this with an example.
%\looseness=-1

@@

By treating $P$ as both data and pattern graphs, compute the maximum match relation $M$ in $P$ for $P$, via graph simulation.
Then pattern $P$ is satisfiable iff for each $(u, v)\in M$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, $x_v \leq y_u$ holds. Observe that the size of $M$ is bounded by $|P|^2$, and pattern graphs are typically small.

@@

\subsection{Batch Algorithm}

\stitle{Handling radius varied balls}. \teamF{} is to find top-$k$ teams within balls $\ball{[v, t]}$, where $v \in V$ and $t \in [1,r]$.
%centered at each node in $G$ with radius $t$ varying from 1 to $r$.
However, it is very costly to construct all $r|V|$ balls, and to compute perfect subgraphs in all of them.
Indeed it is also not necessary, and it only needs to constructs and computes the matches for a number of $|V|$ balls, \ie the set of balls $\ball{[v, r]}$
where $v \in V$ and radius is $r$, and then incrementally computes the perfect subgraphs for balls $\ball{[v, t]}$ ($t \in [1,r-1]$) from the match graphs for ball $\ball{[v, r]}$, as shown below.

@@

When we have the match graph $G_s$ in $\ball{[v, r]}$ for $P$ via graph simulation, to compute the perfect subgraph in $\ball{[v, t]}$ ($t \in [1,r-1]$) for $P$ via team simulation, we need to
(1) first identify the subgraph $G_s^{t}$ in $G_s$ belonging to $\ball{[v, t]}$, which can be easily identified in the process for constructing $\ball{[v, r]}$ without extra computation;
(2) check whether $G_s^{t}$ is already a match graph for $P$ in $\ball{[v, t]}$ via graph simulation; if not, remove the unmatched nodes and edges from $G_s^{t}$ until find the match graph $G'_s$ for $P$ in $\ball{[v, t]}$. This can be achieved by executing an efficient incremental process in~\cite{FanWW13-tods}; and
(3) finally check whether capacity bounds are satisfied. If so, $G'_s$ is the perfect subgraph in $\ball{[v, r]}$ for $P$ via team simulation.

\stitle{Density based ball filtering}. We further reduce the number of balls to speedup the process by adopting the density based filtering technique.
The key idea is to tell whether a ball is possible to produce one of the final top-$k$ matches.

Given a ball $\ball{[v,r]}$, we calculate the upper bound of $\density{\hat{G}_s}$,
where $\hat{G}_s$ is a subgraph of $\ball{[v,r]}$.
If the bound is larger than the current $k$-th result, \ie there is a possibility the for the ball;
Otherwise, we the ball is simply ignored to avoid redundant computations for  team simulation.

The trick part is how to efficiently compute the upper bound of $\density{\hat{G}_s}$ for each ball in $G$.
As the best densest subgraph algorithms are in $O(|\ball{[v,r]}|^3)$ time \cite{maximumDenseSubgraph}, which is costly,
we utilize an important result in~\cite{EVMK12}, shown below.

@@

We are now ready to present our batch algorithm for \teamF{}.

\stitle{Algorithm \grouprec.} As shown in Fig.~\ref{alg-grouprec}, it takes input as $P$, $G$, and two integers $r$ and $k$, and outputs the top-$k$ densest perfect subgraphs in $G$ for $P$.
It firstly checks whether $P$ is satisfiable (line 1).
If so, for each ball $\ball{[v,r]}$ in $G$, it computes the maximum core $\ball{}_{C}$ of $\ball{[v,r]}$, and checks whether the early termination condition holds (lines 3-6).
If so, it returns the current top-$k$ densest perfect subgraphs as top-$k$ teams;
otherwise, it computes the perfect subgraph $G_{s}$ of $P$ in $\ball{[v,r]}$ via team simulation by invoking \rgraphsim (line 7, see full version~\cite{fullvldb18}),
an adaption from graph simulation~\cite{infsimu95,FanLMTWW10} and checking capacity bounds (line 8).
It then computes perfect subgraphs $G'_{s}$ of $P$ in inner balls $\ball{[v,t]}$ by invoking \incsim, an extension of the data incremental algorithms in \cite{FanWW13-tods} and checking capacity bounds (lines 9-11).
%Procedure \rgraphsim is deferred to the appendix, which is an adaption from graph simulation~\cite{infsimu95,FanLMTWW10}.}
%by extending from directed to undirected graphs,  incorporating the capacity constraint check, and only maintaining the capacity bounds satisfied perfect subgraphs.

\stitle{Correctness \& complexity analyses}. The correctness of \grouprec is assured by the following.
%(1) There is a unique perfect subgraph in each ball of $G$.
(1) The correctness of \rgraphsim (resp. \incsim) can be verified along the same lines as for simulation~\cite{infsimu95} (resp. incremental simulation \cite{FanWW13-tods}).
(2) Theorem~\ref{thm-tsim-radius} and Lemma~\ref{lemma-approximation-bound}.
It takes $O(|P|^2)$ to check pattern satisfiability, $O(|V||P||G|)$ to compute team simulation, $O(r|V||V_{P}||E|)$ to incrementally compute matches in inner balls, and $O(|V||E|)$  to compute the density of the maximum core for $|V|$ balls.
Thus \grouprec is in $O(|P|^2+|V||P||G|+r|V||V_{P}||E|)$. However, actual time is much less due to early termination and that  $O(r|V||V_{P}||E|)$ is the worst case complexity for incremental process, while $r$ is small, \ie 2 or 3.
